Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-17 reanalysis-4-outcome_analysis.qmd
emmeans

# Calculate derived statistics
manual_effects <- manual_effects |>
  mutate(
    CI_Lower = Log_Odds - 1.96 * SE,
    CI_Upper = Log_Odds + 1.96 * SE,
    OR = exp(Log_Odds),
    Z_stat = Log_Odds / SE,
    P_Value = 2 * pnorm(-abs(Z_stat))
  ) |>
  mutate(across(c(Log_Odds, SE, CI_Lower, CI_Upper, OR), ~round(., 4))) |>
  mutate(P_Value = format.pval(P_Value, digits = 4, eps = 0.0001)) |>
  select(-Z_stat)

>>>>

# Calculate derived statistics - check for NAs first
if (all(!is.na(manual_effects$Log_Odds)) && all(!is.na(manual_effects$SE))) {
  manual_effects <- manual_effects |>
    mutate(
      CI_Lower = Log_Odds - 1.96 * SE,
      CI_Upper = Log_Odds + 1.96 * SE,
      OR = exp(Log_Odds),
      Z_stat = Log_Odds / SE,
      P_Value = 2 * pnorm(-abs(Z_stat))
    ) |>
    mutate(across(c(Log_Odds, SE, CI_Lower, CI_Upper, OR), ~round(., 4))) |>
    mutate(P_Value = format.pval(P_Value, digits = 4, eps = 0.0001)) |>
    select(-Z_stat)
} else {
  message("Warning: Some manual effect calculations contain NA values")
  # Add placeholder columns
  manual_effects <- manual_effects |>
    mutate(
      CI_Lower = NA,
      CI_Upper = NA,
      OR = NA,
      P_Value = NA
    )
}
